---
title: "Rogue Data"
output: html_document
date: Replicathon 2017
author: Melissa Ortiz
        Giovanni Colon
        Johnathan Lopez
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
library(plyr)
library(dplyr)
library(reshape2)
```

## Instructions:

In this R Markdown document, you and your team will create a fully reproducible analysis with the goal of assessing and interpreting the replicability of two pharmacogenomic experiments. This document should contain all of the text and code of your analyses, which will allow others to run, interpret, and reuse your work.

The questions below will help guide you in your analyses and interpretation of results. You don't need to answer every question, but for the problems you do complete, make sure that you completely justify your conclusions by explaining your reasoning and including numerical summaries and data visualizations wherever possible. There are four tutorials (also R Markdown documents) that will help you learn new tools to tackle these problems, and the questions are divided into four sections corresponding to the tutorials (though many overlap with more than one tutorial). If questions arise during your analyses that do not fit into these problems, feel free to include those as well. 

For each answer, include text by simply typing below the question. Include code in code blocks (include three back ticks at the start and end of each code block):

```{r}
#Your code goes here
```

You may find it helpful to use the version control and code sharing system called GitHub to work together with your team so that all of you can edit the same document and keep track of its changes. Here is a [setup guide](https://github.com/datasciencelabs/2016/blob/master/lectures/git-and-github/setting-up-git.Rmd) and [brief introduction to Git and GitHub](https://github.com/datasciencelabs/2016/blob/master/lectures/git-and-github/version-control.Rmd) from another course. The mentors will be able to help if you run into problems. 

## Questions:
```{r}
rawFile <- "rawPharmacoData.csv"
summarizedFile <- "summarizedPharmacoData.csv"
rawSummaryFile <- "summarizedPharmacoData.csv"
pharmacoData <- read.csv(rawFile)
phSummData <- read.csv(rawSummaryFile)

cellLinesSummary <- read.csv("summarizedPharmacoData.csv", header=TRUE)
str(cellLinesSummary)
```

### Exploratory analysis of pharmacogenomic data

1. How many cell-lines are contained in the data?

```{r CELL LINES}
length(levels(pharmacoData$cellLine))

```
2. What drug concentrations were used in each study?
```{r quest4}
tapply( pharmacoData$concentration, pharmacoData$study, function(x){
        length( unique( x ) )
    })

ggplot( pharmacoData, aes( log2(concentration) ) ) +
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)

```

3. Histograms, appart from telling how is the data
distributed, can also make evident potential
problems with the data. Plot a histogram
of drug viabilities. Does it look as one would
expect from the description of the data?

```{r }
## VIABILITY DISTRIBUTION BY STUDY
ggplot( pharmacoData, aes( viability ) )+
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)

## VIABILITY LOG2 DISTRIBUTION BY STUDY
ggplot( pharmacoData, aes( log2(viability) ) )+
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)

## VIABILITY DISTRIBUTION BY STUDY
ggplot( pharmacoData, aes( viability, group=study, colour=study) ) +
    geom_density(fill="white", lwd=2, alpha=0.1) + xlim(0, 170)

## VIABILITY LOG2 DISTRIBUTION BY STUDY
ggplot( pharmacoData, aes( log2(viability), group=study, colour=study) ) +
    geom_density(fill="white", lwd=2, alpha=0.1)


```

4. How many viability data points are within the
expected range according to the definition of viability (e.g. above 0 
and below 100)? Try to come up with explanations about
the values that are out of range. Are these due to technical
issues? Biology?
```{r, echo=TRUE}
## VIABILITY RANGE
range( pharmacoData$viability )
## TOTAL DATA POINTS
length( pharmacoData$viability)
## < 0 DATA POINTS
sum( pharmacoData$viability < 0 )
## > 100 DATA POINTS
sum( pharmacoData$viability > 100 )
## DATA POINTS ACCORDING TO DEFINITION OF VIABILITY
length( pharmacoData$viability) - sum( pharmacoData$viability < 0 ) - sum( pharmacoData$viability > 100 )

```

5. Read the csv file containing the summarized data files. What kind
of variables are in the data? What does each column represents?
```{r}
## READ CSV FILE
rawSummaryFile <- "summarizedPharmacoData.csv"
phSummData <- read.csv(rawSummaryFile)

summary(phSummData)
# Diferentes Lineas Celulares
# Drugs
# Inhibitory Concentration 50%  CCLE Study
# Area Under The Curve CCLE Study
# Inhibitory Concentration 50%  GDSG Study
# Area Under The Curve GDSG Study
head(phSummData)

```

6. Plot a histogram of the viability scores as a function of the drug
doses. Are stronger drug concentrations consistent with lower viability scores?
```{r}
ggplot( pharmacoData, aes( y=viability, x=log10(concentration), color=study) ) +
    geom_point(cex=0.2) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
    ylim(0, 200)+
    facet_wrap(~drug)


```

```{r}
## GENERATE LINEAR MODELS
fitLinearModel1 <- function(drugA, studyA){
    pharSub <- filter( pharmacoData, drug==drugA, study==studyA)
    pharSub$concentration <- log10( pharSub$concentration )
    fit <- lm( viability~ concentration, pharSub )
    summary(fit)
}

## CALL REGRESSION MODELS BY DRUGS
#17-AAG
fitLinearModel1("17-AAG","CCLE")
fitLinearModel1("17-AAG","GDSC")
## GENERATE LINEAR REGRESSION MODEL PLOTS TO EVALUATE HOW VIABILITY RESPONDS TO CONCENTRATION LEVELS
# R-square Reports the percent od the data explained by this model
# Coef explain the changes in viability due to increasing drug concentration 
ggplot(pharmacoData[pharmacoData$drug=="17-AAG",], aes(x=log10(concentration),y=viability, colour=study)) +  
  geom_point()+
  geom_smooth(method='lm', formula=y~x) +
  ggtitle("17AAG")

```
```{r}

## CALL REGRESSION MODELS BY DRUGS
#paclitaxel
fitLinearModel1("paclitaxel","CCLE")
fitLinearModel1("paclitaxel","GDSC")
ggplot(pharmacoData[pharmacoData$drug=="paclitaxel",], aes(x=log10(concentration),y=viability, colour=study)) +  
  geom_point()+
  geom_smooth(method='lm', formula=y~x) +
  ggtitle("paclitaxel")

```


```{r}

## CALL REGRESSION MODELS BY DRUGS
#Nutlin-3
fitLinearModel1("Nutlin-3","CCLE")
fitLinearModel1("Nutlin-3","GDSC")
ggplot(pharmacoData[pharmacoData$drug=="Nutlin-3",], aes(x=log10(concentration),y=viability, colour=study)) +  
  geom_point()+
  geom_smooth(method='lm', formula=y~x) +
  ggtitle("Nutlin-3")

```

```{r}

## CALL REGRESSION MODELS BY DRUGS
#Sorafenib
fitLinearModel1("Sorafenib","CCLE")
fitLinearModel1("Sorafenib","GDSC")
ggplot(pharmacoData[pharmacoData$drug=="Sorafenib",], aes(x=log10(concentration),y=viability, colour=study)) +  
  geom_point()+
  geom_smooth(method='lm', formula=y~x) +
  ggtitle("Sorafenib")

```


### Using Correlation Measures to Assess Replicability of Drug Response Studies

1. Create a scatterplot for each drug comparing the AUC in GDSC and CCLE for all cell lines (hint: code from Tutorial 2 may help).
```{r Fig2 raw}
cellLinesSummary <- read.csv("summarizedPharmacoData.csv", header=TRUE)

ggplot(aes(x=auc_GDSC, y=auc_CCLE,color=drug), data=cellLinesSummary) +
    geom_point(cex=0.5) + 
    facet_wrap(~drug) +
    xlab("GDSC AUC") +
    ylab("CCLE AUC") 
```
2. Calculate correlation coefficients of the AUC in GDSC and CCLE for each drug (hint: code from Tutorial 2 may help). 
```{r ic50 correlation}
drugCorrsAUC <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_AUC=cor(auc_GDSC,auc_CCLE, method="pearson"),
                                 Spearman_AUC=cor(auc_GDSC,auc_CCLE, method="spearman"))

drugCorrsAUC
```
3. Based on the scatterplot and correlation values, would you say that they tend to agree? Why or why not?
```{r correlation}

ggplot(aes(x=-log10(ic50_GDSC), y=-log10(ic50_CCLE),color=drug), data=cellLinesSummary) +
    geom_point(cex=0.5) + 
    facet_wrap(~drug) +
    xlab("GDSC -log10(IC50)") +
    ylab("CCLE -log10(IC50)") 

drugCorrsIC50 <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_ic50=cor((-log10(ic50_GDSC)/10^6),(-log10(ic50_CCLE)/10^6), method="pearson"),
                                 Spearman_ic50=cor((-log10(ic50_GDSC)/10^6),(-log10(ic50_CCLE)/10^6), method="spearman"))

drugCorrsIC50
```
4. Does the AUC or IC50 suggest more agreement between the studies? 

5. Which drug do you think shows the most consistency between the studies? How about the least? 

6. If you calculated more than one type of correlation coefficient (for example Pearson and Spearman), how do they differ? Which do
you think is a better summary of the consistency between the two studies? 
```{r barplot correlations ic50}
library(reshape2)
drugCorrs <- melt(drugCorrsIC50)
colnames(drugCorrs) <- c("Drug", "Measure", "Correlation")

drugCorrs_IC50 <- drugCorrs[grep("ic50", drugCorrs$Measure),]
ggplot(data=drugCorrs_IC50, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("IC50 Pearson vs. Spearman Coef.")
```
```{r barplot correlations auc}
drugCorrs <- melt(drugCorrsAUC)
colnames(drugCorrs) <- c("Drug", "Measure", "Correlation")

drugCorrs_AUC <- drugCorrs[grep("AUC", drugCorrs$Measure),]
ggplot(data=drugCorrs_AUC, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("AUC Pearson vs. Spearman Coef.")
```

7. We have explored Pearson and Spearman correlation, but what about other correlation measures? For example, you could try out distance correlation, which is sensitive to nonlinear relationships. You can find this measure in the `energy` R package, which you'll need to install and load with the following commands:

    ```{r, eval=FALSE}
   # install.packages("energy")
    library(energy)
    #load(energy)
    #dcor(drugCorrs$Pearson_AUC,drugCorrsAUC$Spearman_AUC)
    #dcor(drugCorrsAUC$Pearson_AUC,dru$Spearman_AUC)
    
   # drugCorrsAUC <- cellLinesSummary %>% 
  #  group_by(drug) %>% summarise(Pearson_AUC=dcor(auc_GDSC,auc_CCLE, method="pearson"),
   #                              Spearman_AUC=dcor(auc_GDSC,auc_CCLE, method="spearman"))

#drugCorrsAUC

    ```

    Then, you can compute distance correlation with the `dcor()` function. How does this correlation measure compare to Pearson and Spearman? Do your conclusions about the agreement between the two studies change at all using this measure?


### Identifying biological factors that influence replicability of pharmacogenomic studies

1. Are there any cell lines that seem to be consistently sensitive? (Hint: look for the 5 cell lines which seem the most resistant in both studies according to the average drug response by AUC; code from Tutorial 3 may help) What effect might this have on your conclusions and interpretations of the agreement between the studies? For example, do you observe any increase in replicability (as measured by correlation of drug response) if you exclude the most resistant cell lines?
```{r, ic50 by cell line}

drugAvg <- cellLinesSummary %>% 
    group_by(cellLine) %>% summarise(mean_ic50_CCLE = mean(-log10(ic50_CCLE/10^6)), 
                        mean_ic50_GDSC = mean(-log10(ic50_GDSC/10^6)),
                        mean_auc_CCLE = mean(auc_CCLE),
                        mean_auc_GDSC = mean(auc_GDSC)) 

ggplot(drugAvg, aes(x=mean_ic50_GDSC, y=mean_ic50_CCLE)) +
    geom_point(alpha=0.6) +
    ggtitle("Average IC50 value by cell line (averaged over drugs)")
```
```{r, auc by cell line}

ggplot(drugAvg, aes(x=mean_auc_GDSC, y=mean_auc_CCLE)) +
    geom_point(alpha=0.6) +
    ggtitle("Average auc value by cell line (averaged over drugs)")
```


2. Classify each cell line as resistant or sensitive to a drug based on its AUC value (Hint: choose a cutoff for which cell lines with AUC below the cutoff are considered sensitive and explain your choice of cutoff(s); code from Tutorial 3 may help). Compare the resistance status of cell lines in GDSC and CCLE for each drug using either a scatterplot of AUC values colored by resistance/sensitivity in each study or a table.
```{r, create sensitivity}
cellLinesSummary <- cellLinesSummary %>% 
              mutate(cutoff = ifelse(drug=="paclitaxel", 0.4, 0.1)) %>%
              mutate(sensitivity_GDSC = factor(ifelse( auc_GDSC < cutoff, "Resistant", "Sensitive")), 
                     sensitivity_CCLE = factor(ifelse( auc_CCLE < cutoff, "Resistant", "Sensitive"))) 

table("GDSC"=cellLinesSummary$sensitivity_GDSC, "CCLE"=cellLinesSummary$sensitivity_CCLE)
```

#### CHEK!!!!!
```{r, auc by sensitivity}

# Paclitaxel Sensitivity Model between Studies
cellLinesSummary <- cellLinesSummary %>% 
              mutate(category = paste(sensitivity_GDSC, sensitivity_CCLE)) %>%
              mutate(category = revalue(category, c("Resistant Resistant" = "Both Resistant",
                                                    "Sensitive Sensitive" = "Both Sensitive",
                                                    "Resistant Sensitive" = "GDSC Resistant / CCLE Sensitive",
                                                    "Sensitive Resistant" = "GDSC Sensitive / CCLE Resistant")))
table(cellLinesSummary$category)

ggplot(aes(x=auc_GDSC, y=auc_CCLE, colour=category), data=subset(cellLinesSummary, drug=="paclitaxel")) +
    geom_point() + 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_hline(aes(yintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    geom_vline(aes(xintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    ggtitle("Drug Paclitaxel")

# 17-AAG Sensitivity Model between Studies
cellLinesSummary <- cellLinesSummary %>% 
              mutate(category = paste(sensitivity_GDSC, sensitivity_CCLE)) %>%
              mutate(category = revalue(category, c("Resistant Resistant" = "Both Resistant",
                                                    "Sensitive Sensitive" = "Both Sensitive",
                                                    "Resistant Sensitive" = "GDSC Resistant / CCLE Sensitive",
                                                    "Sensitive Resistant" = "GDSC Sensitive / CCLE Resistant")))
table(cellLinesSummary$category)

ggplot(aes(x=auc_GDSC, y=auc_CCLE, colour=category), data=subset(cellLinesSummary, drug=="17-AAG")) +
    geom_point() + 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_hline(aes(yintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    geom_vline(aes(xintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    ggtitle("Drug 17-AAG")

# Nutlin-3 Sensitivity Model between Studies
cellLinesSummary <- cellLinesSummary %>% 
              mutate(category = paste(sensitivity_GDSC, sensitivity_CCLE)) %>%
              mutate(category = revalue(category, c("Resistant Resistant" = "Both Resistant",
                                                    "Sensitive Sensitive" = "Both Sensitive",
                                                    "Resistant Sensitive" = "GDSC Resistant / CCLE Sensitive",
                                                    "Sensitive Resistant" = "GDSC Sensitive / CCLE Resistant")))
table(cellLinesSummary$category)

ggplot(aes(x=auc_GDSC, y=auc_CCLE, colour=category), data=subset(cellLinesSummary, drug=="Nutlin-3")) +
    geom_point() + 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_hline(aes(yintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    geom_vline(aes(xintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    ggtitle("Drug Nutlin-3")

# TAE684 Sensitivity Model between Studies
cellLinesSummary <- cellLinesSummary %>% 
              mutate(category = paste(sensitivity_GDSC, sensitivity_CCLE)) %>%
              mutate(category = revalue(category, c("Resistant Resistant" = "Both Resistant",
                                                    "Sensitive Sensitive" = "Both Sensitive",
                                                    "Resistant Sensitive" = "GDSC Resistant / CCLE Sensitive",
                                                    "Sensitive Resistant" = "GDSC Sensitive / CCLE Resistant")))
table(cellLinesSummary$category)

ggplot(aes(x=auc_GDSC, y=auc_CCLE, colour=category), data=subset(cellLinesSummary, drug=="TAE684")) +
    geom_point() + 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_hline(aes(yintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    geom_vline(aes(xintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    ggtitle("Drug TAE684")

```

```{r, sensitivity all drugs}
ggplot(aes(x=auc_GDSC, y=auc_CCLE, colour=category), data=cellLinesSummary) +
    geom_point(cex=0.1) + 
    facet_wrap(facets=~drug) +
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_hline(aes(yintercept=cutoff), colour="grey", alpha=0.75, lty=2) +
    geom_vline(aes(xintercept=cutoff), colour="grey", alpha=0.75, lty=2) 
```

3. Compute the Matthews correlation coefficient for sensitivity status (from #2) of cell lines in GDSC and CCLE for each drug (Hint: code from Tutorial 3 may help). 
```{r, matthews}
# Function to calculate the MCC from two vectors with possible values "Sensitive" and "Resistant"
mcc <- function (study1, study2)
{
  BS <- sum(study1 == "Sensitive" & study2 == "Sensitive") 
  BR <- sum(study1 == "Resistant" & study2 == "Resistant") 
  SR <- sum(study1 == "Sensitive" & study2 == "Resistant") 
  RS <- sum(study1 == "Resistant" & study2 == "Sensitive") 
  
  if (BS+SR == 0 | BS+RS == 0 | BR+SR == 0 |  BR+RS ==0){
    mcc <- ((BS*BR)-(SR*RS)) 
  }else{
    mcc <- ((BS*BR)-(SR*RS)) / sqrt(exp((log(BS+SR)+log(BS+RS)+log(BR+SR)+log(BR+RS))))
  }
  return(mcc)
}

drugCorrsMatt <- cellLinesSummary %>% 
  group_by(cellLine) %>% 
  summarise(matthews_corr=mcc(sensitivity_GDSC, sensitivity_CCLE))

drugCorrsMatt

ggplot(data=drugCorrsMatt, aes(x=cellLine, y=matthews_corr)) +
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Drug")+
  ylab("Matthews Correlation Coefficient")

```

4. Are there any drugs for which most or all cell lines seem to be resistant in both studies (Hint: for each cell line, look at its average response across all drugs; code from Tutorial 3 may help)? If so, what are the correlation values for these drugs? What do these results imply about the replicability of these studies?

* **No effect**: minimal observed resposne for all cell lines
    + sorafenib
    + erlotinib
    + PHA-665752
* **Narrow effect**: response in only a small subset of cell lines
    + nilotinib
    + lapatinib
    + nutlin-3
    + PLX44720
    + crizotinib
    + PD-0332991
    + AZD0530
    + TAE684
* **Broad effect**: response in a large number of cell lines
    + AZD6244
    + PD-0325901
    + 17-AAG
    + paclitaxel
```{r, matthews by drug groups}
# Function to calculate the MCC from two vectors with possible values "Sensitive" and "Resistant"
mcc <- function (study1, study2)
{
  BS <- sum(study1 == "Sensitive" & study2 == "Sensitive") 
  BR <- sum(study1 == "Resistant" & study2 == "Resistant") 
  SR <- sum(study1 == "Sensitive" & study2 == "Resistant") 
  RS <- sum(study1 == "Resistant" & study2 == "Sensitive") 
  
  if (BS+SR == 0 | BS+RS == 0 | BR+SR == 0 |  BR+RS ==0){
    mcc <- ((BS*BR)-(SR*RS)) 
  }else{
    mcc <- ((BS*BR)-(SR*RS)) / sqrt(exp((log(BS+SR)+log(BS+RS)+log(BR+SR)+log(BR+RS))))
  }
  return(mcc)
}

### GENERATE DRUG GROUPS
SummaryCM<-cellLinesSummary
drugGroups<-rep(NA,dim(SummaryCM)[1])

#for (i in 1:dim(SummaryCM)[1]){
#  drugGroups[i]<- ifelse(SummaryCM$drug == "sorafenib","No effect",
#                  ifelse(SummaryCM$drug == "erlotinib","No effect",
#                  ifelse(SummaryCM$drug == "PHA-665752","No effect",
#                  ifelse(SummaryCM$drug == "AZD6244","Broad effect",
#                  ifelse(SummaryCM$drug == "PD-0325901","Broad effect",
#                  ifelse(SummaryCM$drug == "17-AAG","Broad effect",
#                  ifelse(SummaryCM$drug == "paclitaxel","Broad effect","Narrow effect")))))))
#}

for (i in 1:dim(SummaryCM)[1]){
  drugGroups[i]<-ifelse(SummaryCM$drug[i] %in% c("sorafenib","erlotinib","PHA-665752"),"No effect",
    ifelse(SummaryCM$drug[i] %in% c("AZD6244","PD-0325901","17-AAG","paclitaxel"), "Broad effect","Narrow effect"))
}

SummCM<-data.frame(SummaryCM,drugGroups)
SummCM$drugGroups<-as.factor(SummCM$drugGroups)

drugCorrsMattDG <- SummCM %>% 
  group_by(drugGroups) %>% 
  summarise(matthews_corr=mcc(sensitivity_GDSC, sensitivity_CCLE))

drugCorrsMattDG

ggplot(data=drugCorrsMattDG, aes(x=drugGroups, y=matthews_corr, fill=drugGroups)) +
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Drug Groups")+
  ylab("Matthews Correlation Coefficient by Drug Groups")

```
5. Compare the Matthews correlation coefficient values by drug classes defined in Tutorial 3 (No effect, Narrow effect, Broad effect). Which drug class shows the most agreement between the studies? 

6. Would you say that the sensitivity results for the two studies tend to agree?

7. For one of the targeted drugs, examine the cell lines that were sensitive ih the CCLE and/or GDSC. See if you can find out what types of cells these are by searching the online Cancer Cell Line Encyclopedia http://www.broadinstitute.org/ccle (this will prompt you to register with a username, password, and email address. If you prefer, you can also search the cell line on other websites). See if you can find out what types of cancers this drug is targeted for using the NCI cancer drug database at https://www.cancer.gov/about-cancer/treatment/drugs. Does the list of cell lines found to be sensitive in the two studies agree with this?

### Modeling the relation between two variables (drug concentration vs viability)

4. Summarize the viability curves of all the drugs in each cell-line using the slope of linear model. Is the slope of the linear regression informative of the drug response? Can we improve the replicability of the studies by using the value of the slope instead of IC50s or AUCs? 
```{r}

fitLinearModel <- function(drugA, cellLineA, studyA){
    pharSub <- filter( pharmacoData, drug==drugA, cellLine==cellLineA, study==studyA)
    pharSub$concentration <- log10( pharSub$concentration )
    fit <- lm( viability~ concentration, pharSub )
    fit
}

linearModelCCLE1 <- fitLinearModel( "17-AAG", "H4", "CCLE" )
slope1 <- coefficients( linearModelCCLE1 )["concentration"]
linearModelGDSC1 <- fitLinearModel( "17-AAG", "H4", "GDSC" )
slope2 <- coefficients( linearModelGDSC1 )["concentration"]

## drug 17-AAG ... cellLines H4
slope1
slope2

summary(linearModelCCLE1)
summary(linearModelGDSC1)

## drug Nilotinib ... cellLines 22RV1
linearModelCCLE2 <- fitLinearModel( "Nilotinib", "22RV1", "CCLE" )
coefficients( linearModelCCLE2 )["concentration"]
linearModelGDSC2 <- fitLinearModel( "Nilotinib", "22RV1", "GDSC" )
coefficients( linearModelGDSC2 )["concentration"]


summary(linearModelCCLE2)
summary(linearModelGDSC2)
```



## Discussion:

Summarize the main findings of your analyses in the previous four sections here. 

